Plot-figure-X

### 2019-01-17 code/pacific-figure-andrew-temp/plot-figure-x.Rmd

# plot the data z-scored by group

p4 <-  ggplot(merged_whales, aes(x = day_no_f, y = z.d13C.obs)) + 
  facet_wrap(~whale_ID) + 
  geom_line(col = "red") + 
  geom_point(col = "red", size = 1) + 
  geom_line(aes(x = day_no, y = z.d13C.sim), col = "black") + 
  xlab("Day number") + 
  ylab("z-scored d13C")

@@

ggsave("pacific-fits.pdf", plot = p4)
```

>>>>

# plot the data z-scored by group
p4 <-  ggplot(merged_whales, aes(x = day_no_f, y = z.d13C.obs)) + 
  facet_wrap(~whale_ID) + 
  geom_line(col = "black") + 
  geom_point(col = "black", size = 1) + 
  geom_line(aes(x = day_no, y = z.d13C.sim), col = "grey30") + 
  xlab("Day number") + 
  ylab(expression(paste("z-scored ", delta^{13}, "C"))) + 
  theme_classic() + 
  theme(strip.background = element_rect(colour=NA, fill=NA))

@@

ggsave("pacific-fits-zscore.eps", plot = p4)

# = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
# Also try to plot the raw data but shifted and with 
# a second y-axis as per Figure-2-code.R
# AJ - THIS IS MORE DIFFICULT THAN A QUICK BIT OF CODE CAN FIX 
# AS THE SHIFT NEEDS TO BE APPLIED SEPARATELY TO EACH WHALE AND HENCE
# FACET. IM GOING TO COMMENT OUT AND STICK WITH THE Z-SCORED OPTION 
# JUST ABOVE.

# add the d15N data but need to scale it to d13C
# v_shift <- mean(merged_whales$d13C.x) - mean(merged_whales$TL2)
# 
# p5 <-  ggplot(merged_whales, aes(x = day_no_f, y = d13C.x)) + 
#   facet_wrap(~whale_ID) + 
#   geom_line(col = "red") + 
#   geom_point(col = "red", size = 1) + 
#   geom_line(aes(x = day_no, y = TL2), col = "black") + 
#   xlab("Day number") + 
#   ylab(expression(paste(delta^{13}, "C (\u2030) Observed"))) + 
#   scale_y_continuous(
#     sec.axis = sec_axis(~.+v_shift, 
#                         name = expression(paste(delta^{13}, 
#                                                 "C (\u2030) Simulated"))))
# 
# print(p5)
# 
# ggsave("pacific-fits-shifted.eps", plot = p4)
